---
title: "Matrix plot example"
output:
  pdf_document: default
  html_document: default
---

Copyright (C) 2018 Steven G. Rozen and Mi Ni Huang
 
The code is released under GPL-3
https://www.gnu.org/licenses/gpl-3.0.en.html
you can redistribute it and/or modify it under the terms of the
GNU General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option)
any later version.
 
This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

Contact: steverozen@gmail.com


## Set current working directory to the matrix-plot folder
```{r}
CURRENT <- paste(getwd(),"/",sep="")
INPUT <- paste(CURRENT,"example_input/",sep="") ### Directory for INPUT data
```
## Load matrix plot functions
See documentations for functions in "matrix_plot_functions_v0.1.R"
```{r}
source('matrix_plot_functions_v0.1.R')
```
## Load PCAWG WGS assignment and signature aetiologies
```{r}
load(paste0(INPUT, 'PCAWG_Sigprofiler_assignment.RData'))
load(paste0(INPUT,'PCAWG_Sigprofiler_aetiology.RData'))
```
## Filter for samples with > 0.9 accuracy and 100 mutations
```{r}
filtered.exp.data <- filter.samples(exp.data)
```
## Generate matrices for plotting
```{r}
all.mats <- exp.data.to.mats(filtered.exp.data)
```
## Define mutation rate breaks
```{r}
mut.rate.ref <- c(0.0, 0.05, 0.1, 0.25, 0.5, 1, 2.5, 5, 10, 25)
names(mut.rate.ref) <- mut.rate.ref
```
## Plot matrix: adjust the size of the pdf based on the size of input matrices 
```{r}
cairo_pdf('example_output_matrix.pdf',  width=11.2677, height=10.6929)
par(mar=c(3.2, 2.7, 3.3, 23.2))
## remove sig 27, 43, 45 ~ 60: likely aritfact
mat1 <- all.mats$sample.proportion.mat[-c(32,48,50:65),]
mat2 <- all.mats$mut.median.load.mat[-c(32,38,50:65),]
cancer.names<-sort(colnames(mat1))
matrix.plot(mat1, mat2, all.mats$n.samples, etiology, mut.rate.ref=mut.rate.ref, 
            cancer.names=cancer.names, size.legend=TRUE, color.legend='right')
dev.off()
```
